landlord

### 2022-11-14 src/landlord.Rmd
saved data to google sheets in r folder on google drive
added function to print datatable. Double checked landlord policy

library(googlesheets4)
library(janitor)
library(tidyverse)
library(kableExtra)

@@

```{r}
#If there is rent control, immediately disqualify location (set score to -999)
for (j in 1:size[1]) {
  if(MSA_landlord_data$rent_control[j] == "Y"){
    MSA_landlord_data$landlord_score[j] = -999
  }
}
```

>>>>

library(googlesheets4)
library(janitor)
library(tidyverse)
library(kableExtra)
library(DT)

@@

```{r}
#If there is rent control, immediately disqualify location (set score to -999)
for (j in 1:size[1]) {
  if(MSA_landlord_data$rent_control[j] == "Y"){
    MSA_landlord_data$landlord_score[j] = -999
  }
}

datatable(MSA_landlord_data, extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
```
